Automated Topic Naming

### 2011-09-03 ese/ese.tex
writing

\subsection{Do different developers work on different NFRs?}
We did a t-test to assess whether there was statistically significant differences in the types of NFRs developers chose to work on, for the PostgreSQL project only. 
\todo{add more, figure}

*** We also clustered the authors by similarity and we found that
among some of the most prolific postgresql authors, their NFR focus
was distinctly different *** Some confounds are that postgresql
authors commit the patches of others.

>>>>

\subsection{Do different developers work on different NFRs?}

%data/clusters.R

We wanted to see how similar developers were to each other in terms of
the NFRs that worked on. First we did pairwise $X^2$ (chi-squared)
tests and Kolmogorov-Smirnov tests for each developer pair and we
found that $3/10$ of these tests the developers were significantly
different, that is their distributions were not similar. This implies
that there are authors who focus on different NFRs or different
proportion of NFRs.

In Figure \ref{fig:authorcluster} we clustered developers using the
Ward method of Hierarchical clsutering. We've clustered the authors
into 2 clusters and 5 clusters.

\begin{figure}
  \centering
  \includegraphics[width=.9\textwidth]{figures/postgresql-author-cluster}
  \caption{PostgreSQL Author Clusters: Authors clustered by cosine
    distance of their NFR contributions}
\label{fig:authorcluster}
\end{figure}
